\section{Introduction}
\label{sec:introduction}

Wavetable oscillators store one period of a waveform and advance a read pointer modulo the table length.
If $x[0]\neq x[L-1]$, the wrap is a hard discontinuity. Under cyclic playback it becomes a periodic click whose spectrum is broadband and locked to the fundamental.
The same geometry appears whenever a short loop buffer is tiled for listening or for objective evaluation.
We call the repair task \emph{cycle-local seam restoration}: edit a neighborhood of the wrap (and optionally a lightweight residual cell over the period) so that multi-period playback matches an ideal reference that never opens the wrap cliff.
That outer agreement is what we score as audio denoising for this periodic artifact class.

Classical virtual-analog practice already supplies seam-local tools.
Alias-free BLIT/BLEP-style synthesis~\cite{stilson1996}, PolyBLEP / fractional-delay antialiasing~\cite{nam2009polyblep}, differentiated polynomial waveforms~\cite{valimaki2010dpw}, and BLAMP corner corrections~\cite{esqueda2016blamp} reduce wrap and geometric discontinuity energy in-band.
Those operators act locally.
They leave open which bake parameters and which residual cell, if any, minimize prolonged tiled error against a no-cliff ideal.
Label-free restoration work such as Noise2Noise shows that useful reconstructors can be ranked without paired clean targets when the evaluation geometry is explicit~\cite{lehtinen2018}.
Speech-domain Noise2Noise denoisers extend that idea to audio waveforms~\cite{kashyap2021n2n}.
Mixture-invariant unsupervised separation likewise avoids paired clean stems for ranking~\cite{wisdom2020}.
On the search side, NAS surveys~\cite{elsken2019}, RL controllers~\cite{zoph2017nas,pham2018}, aging evolution~\cite{real2017large,real2019}, population-based hyperparameter schedules~\cite{jaderberg2017}, CMA-ES tutorials~\cite{hansen2016cmaes}, and evolution-guided policy gradients~\cite{khadka2018} motivate a hybrid outer loop: GA for population diversity, PPO for discrete architecture edits~\cite{schulman2017}, and PBT-style exploit--mutate on elites.
Platform-aware and progressive NAS add compute-aware search priors~\cite{tan2019mnasnet,liu2018pnas}.
MoE soft gates suggest routing among heterogeneous tiny cells under one residual score~\cite{shazeer2017}.
Waveform separation nets (Wave-U-Net, Conv-TasNet, dual-path RNN, SepFormer) and audio DL surveys inform the searchable cell family at bake-scale width~\cite{stoller2018,macartney2018,luo2019,luo2020dprnn,subakan2021,purwins2019,gong2021ast}, with U-Net / ResNet / attention primitives as block ancestors~\cite{ronneberger2015,he2016resnet,vaswani2017,jansson2017}.

The contribution is a meta-learning protocol for this periodic instance.
An outer RL+GA(+PBT) loop proposes denoising operator graphs and continuous bake parameters.
Each candidate is scored by a prolonged residual $R\in[0,1]$ (1~=~best) between engine-baked multi-period audio and a procedural ideal tiling.
Paired studio-clean wavetables are not required for every trial.
Differentiable DSP modules~\cite{engel2020} place DualCosine / FIR / MLP seam ops in an interpretable stack.
Bayesian HPO~\cite{snoek2012} informs prior families that compete under the same $R$.
A CUDA overnight campaign (PPO+GA+PBT+NAS, depth and MoE biases) has passed a $5{,}000$-iteration clean gate with champion $R\approx 0.9909$ versus DualCosine $\approx 0.8166$ on the runner geometry.
Held-out matrices and declared long-horizon mean-$R$ remain deferred until the full budget completes.

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{Problem framing.} Cast wavetable wrap discontinuity / cycle-local seam restoration as audio denoising under prolonged tiled evaluation, separating seam-local diagnostics from residual $R$.
  \item \textbf{Hybrid DenoiseOpt outer loop.} Specify RL+GA(+PBT) search over discrete operator graphs and continuous bake parameters, with named branches (GA crossover, PPO mutation, PBT exploit, MoE soft gates).
  \item \textbf{OA literature protocol.} Separate used versus screened prior work for audio denoise cells and RL--evolutionary hybrids, grounded on downloaded OA PDFs only.
  \item \textbf{Open evaluation path.} Release companion code for the synthesizer engine and meta search, with frozen $5$k-gate figures and matched classical-vs-AI benches.
\end{enumerate}

Section~\ref{sec:related_work} organizes related work by mechanism.
Sections~\ref{sec:methods}--\ref{sec:experiments} outline the residual objective and search protocol.
Results report the $5$k-gate freeze and inference benches.
