\section{Methods}
\label{sec:methods}

\paragraph{Notation.}
Throughout, $x\in\mathbb{R}^{L}$ is the stored single-period wavetable (raw engine input).
$y=\Theta(x;\theta)$ is the engine-baked cycle after seam ops and optional residual cells with parameters $\theta$.
$r^{\star}$ is a procedural multi-period ideal from the same seed with open-wrap cliffs withheld (not a studio-clean recording).
$R\in[0,1]$ is the prolonged residual score defined below ($1$~=~best).
These symbols are fixed for the residual objective. They do not follow the Noise2Noise clean/noisy pair convention.

\paragraph{Residual score.}
With tiling length $N$ (typically $N{=}16$),
\begin{equation}
R=\mathrm{clamp}\!\left(1-\frac{\mathrm{rms}(y_{\mathrm{tiled}}-r^{\star}_{\mathrm{tiled}})}{\max(\mathrm{rms}(r^{\star}_{\mathrm{tiled}}),\varepsilon)},\,0,\,1\right).
\end{equation}
By construction $R\in[0,1]$ with $1$ best. Soft shape gates (when enabled) down-weight mid-cycle damage relative to seam-local error.

\paragraph{Searchable operator.}
Candidates combine classical seam ops (DualCosine, polish, soft seam, FIR blends) with tiny residual cells (MLP/FIR/U-Net-lite/attention-lite) and optional MoE soft gates.
Bake parameters $\theta$ live in a bounded box. Architecture strings are discrete graphs over those ops.

\paragraph{Hybrid outer loop.}
Each iteration may (i)~run GA tournament selection with crossover/mutation, (ii)~sample PPO actions that edit ops/hyperparameters, (iii)~apply PBT-style exploit--mutate on elites, and (iv)~evaluate literature-combo priors.
Selection is always by residual $R$ (and logged auxiliaries).
The live overnight configuration is tagged \texttt{PPO+GA+PBT+NAS+depth+MoE} with population size $12$, plateau adaptation every $1000$ iterations, and CUDA scoring on an RTX~3090.
