%% DenoiseOpt paper -- arXiv-style double-column preprint
%% Template: article[twocolumn] + local arxiv-twocolumn.sty
%% Bibliography policy: OA-only (every \\bibitem has a downloadable OA PDF).
\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{arxiv-twocolumn}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{placeins}
\usepackage{amsmath,amssymb}
\usepackage{xurl}
\usepackage{cite}
\usepackage{balance}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{orcidlink}

\title{Unsupervised Deep Audio Denoising Algorithms via\\
Hybrid Reinforcement Learning and Genetic Algorithm Meta-Learning}
\author{%
  Julian~M.~Kleber\,\orcidlink{0000-0001-5518-0932}\\[2pt]
  \normalsize
  Email:
  \href{mailto:julian.m.kleber@gmail.com}{\texttt{julian.m.kleber@gmail.com}}
}
\date{19 July 2026}
\newcommand{\papershorttitle}{Unsupervised Deep Audio Denoising}

\begin{document}

\twocolumn[{%
  \maketitle
  \begin{center}\footnotesize
    Code (ReelSynth engine + DenoiseOpt meta-search):
    \url{https://github.com/reeldemo/reelsynth},
    \url{https://github.com/reeldemo/denoise-opt-meta}
  \end{center}
  \begin{abstract}
    When a single-period wavetable (or any short cyclic buffer) is played with phase wrap,
    a sample discontinuity at the period boundary injects a broadband transient that repeats
    at the fundamental. We treat this cycle-local seam crackle as an audio denoising problem:
    seam-local operators (DualCosine crossfade, polish, FIR blends, optional tiny residual cells)
    are baked into the period, then judged by a prolonged residual $R\in[0,1]$ against an ideal
    multi-period tiling that withholds the open-wrap cliff (1~=~best).
    We call the residual-scored hybrid search \textbf{DenoiseOpt}.
    An outer hybrid meta-search interleaves GA tournament updates with proximal policy
    optimization (PPO) architecture proposals,
    optional PBT exploit--mutate schedules, and MoE soft gates over heterogeneous bake cells.
    Candidates need not be paired with studio-clean waveforms for every trial.
    On a matched CUDA inference bench, a compact favorite reaches $R\approx 0.991$ versus
    DualCosine $R\approx 0.820$ ($\Delta R\approx{+}0.171$).
    A live GPU hybrid campaign has passed $5{,}000$ clean iterations with champion
    $R\approx 0.9909$ against DualCosine $\approx 0.8166$ on the runner geometry.
    Declared long-horizon mean-$R$ tables remain open until the full budget finishes.
  \end{abstract}
  \keywords{unsupervised learning $\cdot$ audio denoising $\cdot$ DenoiseOpt $\cdot$ neural architecture search $\cdot$ reinforcement learning $\cdot$ genetic algorithms $\cdot$ wavetable synthesis $\cdot$ wrap discontinuity $\cdot$ meta-learning}
  \vspace{0.6em}
}]

\input{subsections/introduction}
\input{subsections/related_work}
\input{subsections/methods}
\input{subsections/experiments}
\input{subsections/results}
\input{subsections/discussion}
\input{subsections/tooling}
\input{subsections/limitations}
\input{subsections/conclusion}

\FloatBarrier
\clearpage
\raggedbottom
\balance
{\footnotesize
\setlength{\baselineskip}{11.5pt}
\begin{thebibliography}{99}
\setlength{\itemsep}{0.25ex plus 0.05ex}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}

\bibitem{stilson1996}
T.~Stilson and J.~O.~Smith.
\newblock Alias-free digital synthesis of classic analog waveforms.
\newblock In \emph{Proc.\ ICMC}, 1996.
\newblock \url{https://ccrma.stanford.edu/~stilti/papers/blit.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{esqueda2016blamp}
F.~Esqueda, V.~V\"alim\"aki, and S.~Bilbao.
\newblock Rounding corners with BLAMP.
\newblock In \emph{Proc.\ DAFx}, 2016.
\newblock \url{https://www.dafx.de/paper-archive/2016/dafxpapers/18-DAFx-16_paper_33-PN.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{valimaki2010dpw}
V.~V\"alim\"aki, J.~Nam, J.~O.~Smith, and J.~S.~Abel.
\newblock Alias-suppressed oscillators based on differentiated polynomial waveforms.
\newblock \emph{IEEE Trans.\ Audio, Speech, Lang.\ Process.}, 2010.
\newblock Author PDF: \url{https://mac.kaist.ac.kr/pubs/ValimakiNamSmithAbel-taslp2010.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{nam2009polyblep}
J.~Nam, V.~V\"alim\"aki, J.~S.~Abel, and J.~O.~Smith.
\newblock Efficient antialiasing oscillator algorithms using low-order fractional delay filters.
\newblock In \emph{Proc.\ DAFx}, 2009.
\newblock \url{https://ccrma.stanford.edu/~juhan/pubs/jnam-dafx09.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{lehtinen2018}
J.~Lehtinen et al.
\newblock Noise2Noise: Learning image restoration without clean data.
\newblock In \emph{ICML}, 2018.
\newblock \href{https://arxiv.org/abs/1803.04189}{arXiv:1803.04189}.
\newblock Access: \textbf{[OA]}.

\bibitem{kashyap2021n2n}
M.~M.~Kashyap, A.~Tambwekar, K.~Manohara, and S.~Natarajan.
\newblock Speech denoising without clean training data: A Noise2Noise approach.
\newblock In \emph{INTERSPEECH}, 2021.
\newblock \url{https://www.isca-archive.org/interspeech_2021/kashyap21_interspeech.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{engel2020}
J.~Engel, L.~Hantrakul, C.~Gu, and A.~Roberts.
\newblock DDSP: Differentiable digital signal processing.
\newblock In \emph{ICLR}, 2020.
\newblock \href{https://arxiv.org/abs/2001.04643}{arXiv:2001.04643}.
\newblock Access: \textbf{[OA]}.

\bibitem{purwins2019}
H.~Purwins et al.
\newblock Deep learning for audio signal processing.
\newblock \emph{IEEE J.\ Sel.\ Topics Signal Process.}, 2019.
\newblock \href{https://arxiv.org/abs/1905.00078}{arXiv:1905.00078}.
\newblock Access: \textbf{[OA]}.

\bibitem{stoller2018}
D.~Stoller, S.~Ewert, and S.~Dixon.
\newblock Wave-U-Net: A multi-scale neural network for end-to-end audio source separation.
\newblock In \emph{ISMIR}, 2018.
\newblock \href{https://arxiv.org/abs/1806.03185}{arXiv:1806.03185}.
\newblock Access: \textbf{[OA]}.

\bibitem{macartney2018}
C.~Macartney and T.~Weyde.
\newblock Improved speech enhancement with the Wave-U-Net.
\newblock \href{https://arxiv.org/abs/1811.11307}{arXiv:1811.11307}, 2018.
\newblock Access: \textbf{[OA]}.

\bibitem{jansson2017}
A.~Jansson et al.
\newblock Singing voice separation with deep U-Net convolutional networks.
\newblock In \emph{ISMIR}, 2017.
\newblock \url{https://openaccess.city.ac.uk/id/eprint/19289/1/7bb8d1600fba70dd79408775cd0c37a4ff62.pdf}.
\newblock Access: \textbf{[OA]}.

\bibitem{luo2019}
Y.~Luo and N.~Mesgarani.
\newblock Conv-TasNet: Surpassing ideal time--frequency magnitude masking for speech separation.
\newblock \emph{IEEE/ACM TASLP}, 2019.
\newblock \href{https://arxiv.org/abs/1809.07454}{arXiv:1809.07454}.
\newblock Access: \textbf{[OA]}.

\bibitem{luo2020dprnn}
Y.~Luo, Z.~Chen, and T.~Yoshioka.
\newblock Dual-path RNN: Efficient long sequence modeling for time-domain speech separation.
\newblock In \emph{ICASSP}, 2020.
\newblock \href{https://arxiv.org/abs/1910.06379}{arXiv:1910.06379}.
\newblock Access: \textbf{[OA]}.

\bibitem{ronneberger2015}
O.~Ronneberger, P.~Fischer, and T.~Brox.
\newblock U-Net: Convolutional networks for biomedical image segmentation.
\newblock In \emph{MICCAI}, 2015.
\newblock \href{https://arxiv.org/abs/1505.04597}{arXiv:1505.04597}.
\newblock Access: \textbf{[OA]}.

\bibitem{he2016resnet}
K.~He, X.~Zhang, S.~Ren, and J.~Sun.
\newblock Deep residual learning for image recognition.
\newblock In \emph{CVPR}, 2016.
\newblock \href{https://arxiv.org/abs/1512.03385}{arXiv:1512.03385}.
\newblock Access: \textbf{[OA]}.

\bibitem{vaswani2017}
A.~Vaswani et al.
\newblock Attention is all you need.
\newblock In \emph{NeurIPS}, 2017.
\newblock \href{https://arxiv.org/abs/1706.03762}{arXiv:1706.03762}.
\newblock Access: \textbf{[OA]}.

\bibitem{elsken2019}
T.~Elsken, J.~H.~Metzen, and F.~Hutter.
\newblock Neural architecture search: A survey.
\newblock \emph{JMLR}, 2019.
\newblock \href{https://arxiv.org/abs/1808.05377}{arXiv:1808.05377}.
\newblock Access: \textbf{[OA]}.

\bibitem{zoph2017nas}
B.~Zoph and Q.~V.~Le.
\newblock Neural architecture search with reinforcement learning.
\newblock In \emph{ICLR}, 2017.
\newblock \href{https://arxiv.org/abs/1611.01578}{arXiv:1611.01578}.
\newblock Access: \textbf{[OA]}.

\bibitem{pham2018}
H.~Pham et al.
\newblock Efficient neural architecture search via parameter sharing.
\newblock In \emph{ICML}, 2018.
\newblock \href{https://arxiv.org/abs/1802.03268}{arXiv:1802.03268}.
\newblock Access: \textbf{[OA]}.

\bibitem{schulman2017}
J.~Schulman et al.
\newblock Proximal policy optimization algorithms.
\newblock \href{https://arxiv.org/abs/1707.06347}{arXiv:1707.06347}, 2017.
\newblock Access: \textbf{[OA]}.

\bibitem{real2017large}
E.~Real et al.
\newblock Large-scale evolution of image classifiers.
\newblock In \emph{ICML}, 2017.
\newblock \href{https://arxiv.org/abs/1703.01041}{arXiv:1703.01041}.
\newblock Access: \textbf{[OA]}.

\bibitem{real2019}
E.~Real, A.~Aggarwal, Y.~Huang, and Q.~V.~Le.
\newblock Regularized evolution for image classifier architecture search.
\newblock In \emph{AAAI}, 2019.
\newblock \href{https://arxiv.org/abs/1802.01548}{arXiv:1802.01548}.
\newblock Access: \textbf{[OA]}.

\bibitem{jaderberg2017}
M.~Jaderberg et al.
\newblock Population based training of neural networks.
\newblock \href{https://arxiv.org/abs/1711.09846}{arXiv:1711.09846}, 2017.
\newblock Access: \textbf{[OA]}.

\bibitem{khadka2018}
S.~Khadka and K.~Tumer.
\newblock Evolution-guided policy gradient in reinforcement learning.
\newblock In \emph{NeurIPS}, 2018.
\newblock \href{https://arxiv.org/abs/1805.07917}{arXiv:1805.07917}.
\newblock Access: \textbf{[OA]}.

\bibitem{hansen2016cmaes}
N.~Hansen.
\newblock The CMA evolution strategy: A tutorial.
\newblock \href{https://arxiv.org/abs/1604.00772}{arXiv:1604.00772}, 2016.
\newblock Access: \textbf{[OA]}.

\bibitem{shazeer2017}
N.~Shazeer et al.
\newblock Outrageously large neural networks: The sparsely-gated mixture-of-experts layer.
\newblock In \emph{ICLR}, 2017.
\newblock \href{https://arxiv.org/abs/1701.06538}{arXiv:1701.06538}.
\newblock Access: \textbf{[OA]}.

\bibitem{snoek2012}
J.~Snoek, H.~Larochelle, and R.~P.~Adams.
\newblock Practical Bayesian optimization of machine learning algorithms.
\newblock In \emph{NeurIPS}, 2012.
\newblock \href{https://arxiv.org/abs/1206.2944}{arXiv:1206.2944}.
\newblock Access: \textbf{[OA]}.

\bibitem{tan2019mnasnet}
M.~Tan et al.
\newblock MnasNet: Platform-aware neural architecture search for mobile.
\newblock In \emph{CVPR}, 2019.
\newblock \href{https://arxiv.org/abs/1807.11626}{arXiv:1807.11626}.
\newblock Access: \textbf{[OA]}.

\bibitem{liu2018pnas}
C.~Liu et al.
\newblock Progressive neural architecture search.
\newblock In \emph{ECCV}, 2018.
\newblock \href{https://arxiv.org/abs/1712.00559}{arXiv:1712.00559}.
\newblock Access: \textbf{[OA]}.

\bibitem{wisdom2020}
S.~Wisdom et al.
\newblock Unsupervised sound separation using mixture invariant training.
\newblock In \emph{NeurIPS}, 2020.
\newblock \href{https://arxiv.org/abs/2006.12701}{arXiv:2006.12701}.
\newblock Access: \textbf{[OA]}.

\bibitem{subakan2021}
C.~Subakan, M.~Ravanelli, S.~Cornell, M.~Bronzi, and J.~Zhong.
\newblock Attention is all you need in speech separation.
\newblock In \emph{ICASSP}, 2021.
\newblock \href{https://arxiv.org/abs/2010.13154}{arXiv:2010.13154}.
\newblock Access: \textbf{[OA]}.

\bibitem{gong2021ast}
Y.~Gong, Y.-A.~Chung, and J.~Glass.
\newblock AST: Audio spectrogram transformer.
\newblock In \emph{INTERSPEECH}, 2021.
\newblock \href{https://arxiv.org/abs/2104.01778}{arXiv:2104.01778}.
\newblock Access: \textbf{[OA]}.

\bibitem{finn2017}
C.~Finn, P.~Abbeel, and S.~Levine.
\newblock Model-agnostic meta-learning for fast adaptation of deep networks.
\newblock In \emph{ICML}, 2017.
\newblock \href{https://arxiv.org/abs/1703.03400}{arXiv:1703.03400}. \textit{(Screened.)}
\newblock Access: \textbf{[OA]}.

\bibitem{liu2019}
H.~Liu, K.~Simonyan, and Y.~Yang.
\newblock DARTS: Differentiable architecture search.
\newblock In \emph{ICLR}, 2019.
\newblock \href{https://arxiv.org/abs/1806.09055}{arXiv:1806.09055}. \textit{(Screened.)}
\newblock Access: \textbf{[OA]}.

\bibitem{dfossez2019}
A.~D\'efossez et al.
\newblock Demucs: Deep extractor for music sources.
\newblock \href{https://arxiv.org/abs/1911.13254}{arXiv:1911.13254}, 2019. \textit{(Screened.)}
\newblock Access: \textbf{[OA]}.

\bibitem{dfossez2020}
A.~D\'efossez, G.~Synnaeve, and Y.~Adi.
\newblock Real time speech enhancement in the waveform domain.
\newblock In \emph{INTERSPEECH}, 2020. \textit{(Screened.)}
\newblock \href{https://arxiv.org/abs/2006.12847}{arXiv:2006.12847}.
\newblock Access: \textbf{[OA]}.

\bibitem{dfossez2021}
A.~D\'efossez.
\newblock Hybrid spectrogram and waveform source separation.
\newblock \href{https://arxiv.org/abs/2111.03600}{arXiv:2111.03600}, 2021. \textit{(Screened.)}
\newblock Access: \textbf{[OA]}.

\bibitem{kong2021}
Z.~Kong et al.
\newblock DiffWave: A versatile diffusion model for audio synthesis.
\newblock In \emph{ICLR}, 2021.
\newblock \href{https://arxiv.org/abs/2009.00713}{arXiv:2009.00713}. \textit{(Screened.)}
\newblock Access: \textbf{[OA]}.

\bibitem{pascual2017}
S.~Pascual, A.~Bonafonte, and J.~Serr\`a.
\newblock SEGAN: Speech enhancement generative adversarial network.
\newblock In \emph{INTERSPEECH}, 2017. \textit{(Screened.)}
\newblock \href{https://arxiv.org/abs/1703.09452}{arXiv:1703.09452}.
\newblock Access: \textbf{[OA]}.

\end{thebibliography}
}

\end{document}
