\section{Broader impact and reproducibility}
\label{sec:ethics}

\paragraph{Broader impact.}
This work targets cycle-local wavetable seam repair for virtual-analog / software-instrument workflows.
Misuse potential is low. The method does not enhance speech for surveillance, does not remove watermarks from protected media, and operates only on short synthetic periods.
Training and search use procedural sine{+}cliff generators. No private studio stems are required for the reported tables.
The main resource cost is GPU time on a consumer RTX~3090 (order of hours for the $5$k-gate freeze, Table~\ref{tab:compute}).
Authors should not over-claim speech enhancement or production mastering quality from these metrics.

\paragraph{Reproducibility.}
Holdout seed $20{,}260{,}719$. Overnight search seed $1{,}902{,}771{,}841$.
Primary code: \url{https://github.com/reeldemo/reelsynth} (\texttt{scripts/overnight\_gpu\_rl\_arch.py}, \texttt{scripts/bench\_sota\_matrix.py}, \texttt{scripts/metrics\_snr\_sdr.py}).
Paper companion: \url{https://github.com/reeldemo/denoise-opt-meta}.
Dependencies for the CUDA benches: Python~3.12, PyTorch~$2.6$+CUDA~12.4, NumPy/matplotlib. Rust/\texttt{cargo} builds the separate \texttt{sound\_bench} hardness probe.
JSON artifacts under \texttt{brand/artifacts/} (\texttt{sota\_matrix.json}, \texttt{canonical\_eval\_dataset/}, overnight \texttt{history.jsonl}) freeze the numbers in Section~\ref{sec:results}.
PESQ/STOI are omitted for non-speech cycles (domain mismatch). MUSHRA was not run.

\paragraph{Competing interests.}
None to declare.
