\section{Limitations}
\label{sec:limitations}

\paragraph{Scope and evaluation limits.}
The prolonged residual $R$ is defined against a procedural no-cliff sibling and does not capture perceptual quality directly.
Formal listening tests (MOS, MUSHRA) are outside the scope of this work and are deferred to future studies.
PESQ and STOI are excluded because the primary cycles are non-speech synthetic wavetable tiles; speech-quality metrics on sine{+}cliff families would be a domain mismatch.
MUSHRA was not run (requires human listeners).
Any perceptual or speech-proxy secondary study would need separately labeled open-access speech snippets and remains out of scope for this narrow-seam paper.

\begin{itemize}
  \item Residual uses a procedural ideal (no-cliff sibling). Perceptual MOS and listening panels are out of scope.
  \item Bake metrics leave formal listening tests and speech quality metrics to separate studies.
  \item \textbf{PESQ / STOI / MUSHRA deferred.} Primary cycles are non-speech wavetable tiles. Speech metrics would domain-mismatch sine{+}cliff families, so PESQ/STOI numbers are absent here (none invented on synthetic tiles). MUSHRA needs human listeners and was \emph{not run}.
  \item The overnight CUDA runner scores Python \texttt{make\_batch} sine{+}cliff draws. A separate Rust \texttt{sound\_bench} export of 20 family tiles (byte-aligned generator) is a secondary transfer block. The Python generative SOTA matrix is the primary multi-family table.
  \item Per-trial architecture width is capped for overnight throughput. Full Demucs-/diffusion-scale stacks were screened out.
  \item The $5$k-gate freeze reports measured champion and overnight branch-best residuals. Isolated GA/PPO/GA{+}PPO/full re-runs use a short labeled budget (same search seed). Those short runs are a different protocol from the multi-hour freeze.
  \item Classical VA/BLEP anchors use author or proceedings PDFs (\texttt{stilson1996}, \texttt{nam2009polyblep}, \texttt{esqueda2016blamp}).
\end{itemize}

\subsection{Outlook: follow-up publication}
\label{sec:outlook}

A self-contained follow-up can treat \emph{which sounds fail} as the primary object of study: stratified residual heatmaps over the ten procedural families, cliff-size conditioning, and family-specialist or mixture-of-experts denoisers selected by the same RL--GA outer loop.
That paper would cite the present mean-$R$ hybrid protocol as the baseline and ask whether beating $R>0.999$ is mainly an architecture problem or a coverage problem over hard families.
