\section{Related Work}
\label{sec:related_work}

We organize prior work by mechanism.
\textbf{Used} lines are methodological or comparative anchors for residual-scored RL+GA meta-search.
\textbf{Screened} lines were inspected as contrast. They are excluded from the dependency set.
Paraphrases prefer attached abstracts and PDF snippets over title-only citation.

\subsection{Discontinuity control and modular audio DSP}
Alias-free digital synthesis of classic analog waveforms (BLIT/BLEP lineage) states the wrap discontinuity problem for trivial oscillators~\cite{stilson1996}.
PolyBLEP-style fractional-delay corrections give practical antialiasing oscillators for subtractive synthesis~\cite{nam2009polyblep}.
BLAMP corner rounding treats discontinuities in the first derivative (triangular edges, clipping, rectification) without heavy oversampling~\cite{esqueda2016blamp}.
DDSP reframes DSP modules as composable blocks inside learning pipelines~\cite{engel2020}.
We use that framing for small bake/FIR/MLP seam cells.
We do not train end-to-end neural vocoders for every meta trial.
These works are \textbf{used} as domain anchors for the operator vocabulary and for why prolonged cyclic playback is the outer judge.

\subsection{Label-free restoration}
Noise2Noise shows that restoration mappings can be learned from corrupted observations alone by exploiting structure in the corruption process~\cite{lehtinen2018}.
Speech Noise2Noise denoisers apply the same idea to waveforms without clean paired audio~\cite{kashyap2021n2n}.
Mixture invariant training ranks unsupervised separation systems without stem labels~\cite{wisdom2020}.
That philosophy motivates ranking denoise candidates without paired studio-clean wavetable cycles.
The residual compares an engine-baked tiling to a procedural ideal that withholds open-wrap cliffs.
We \textbf{use} this family as conceptual justification for unsupervised residual ranking.
We do not retrain a Noise2Noise CNN on images.

\subsection{Waveform denoising and separation cells}
Deep learning for audio surveys the move from hand-designed features to learned time/frequency models~\cite{purwins2019}.
Wave-U-Net performs end-to-end source separation with multi-scale 1-D U-Nets~\cite{stoller2018}.
Improved Wave-U-Net speech enhancement and singing-voice U-Nets popularized encoder--decoder skips on audio~\cite{macartney2018,jansson2017}.
The original U-Net, ResNet residuals, and Transformer attention supply the block primitives we shrink to bake width~\cite{ronneberger2015,he2016resnet,vaswani2017}.
Conv-TasNet and dual-path RNN demonstrated strong time-domain separation with temporal convolutions and long-context paths~\cite{luo2019,luo2020dprnn}.
SepFormer and audio spectrogram transformers push attention-heavy audio stacks further~\cite{subakan2021,gong2021ast}.
These lines are \textbf{used} as design priors for tiny searchable cells (shallow U-Net / dilated / dual-path / attention blocks under a strict per-trial bake budget).
They are not frozen full-scale separators inside every meta trial.

\subsection{NAS and RL controllers}
Elsken et al.\ taxonomize NAS by search space, strategy, and evaluation cost~\cite{elsken2019}.
Their performance-estimation axis includes lower-fidelity proxies such as shorter training, data subsets, and lower-resolution images~\cite{elsken2019}.
Zoph and Le couple RL controllers to architecture search~\cite{zoph2017nas}.
ENAS adds parameter sharing for efficient discrete search~\cite{pham2018}.
Progressive and platform-aware NAS add staged evaluation and latency-aware rewards~\cite{liu2018pnas,tan2019mnasnet}.
We \textbf{use} this family as the ancestor of RL proposing architecture edits (add/remove/mutate ops, toggle residual-primary, mutate MLP/FIR), scored with prolonged residual.
PPO supplies the clipped-surrogate policy update when the overnight loop logs PPO mutation branches~\cite{schulman2017}.

\subsection{Evolutionary NAS and population schedules}
Large-scale and regularized / aging evolution showed that evolutionary NAS can discover competitive image classifiers when population turnover is carefully regularized~\cite{real2017large,real2019}.
Population Based Training jointly adapts weights and hyperparameters in an asynchronous population~\cite{jaderberg2017}.
Practical Bayesian optimization~\cite{snoek2012} and CMA-ES tutorials~\cite{hansen2016cmaes} inform local Bayesian and continuous evolutionary prior families.
These are \textbf{used} for GA tournament/crossover branches, PBT-style exploit--mutate, and literature-combo priors, implemented at synthesizer-trial scale.

\subsection{Evolutionary reinforcement learning hybrids}
Khadka and Tumer's evolution-guided policy gradient (ERL) interleaves an evolutionary population with an RL actor to mitigate sparse reward and brittle hyperparameters in deep RL~\cite{khadka2018}.
We \textbf{use} ERL as the spirit of interleaving GA population steps with PPO updates at tiny population sizes.
We do not claim a full ERL robotics stack.

\subsection{Mixture-of-experts soft gating}
Sparsely gated MoE layers increase capacity via conditional computation~\cite{shazeer2017}.
We \textbf{use} MoE as motivation for soft gates over heterogeneous seam blocks (e.g., U-Net vs dilated vs attention cells) under residual scoring, at bake-scale widths.

\subsection{Used versus screened}
\label{sec:used-screened}

\paragraph{Used (methodological or comparative anchors).}
\begin{itemize}
  \item Discontinuity / VA lineage:~\cite{stilson1996,esqueda2016blamp,nam2009polyblep}.
  \item Unsupervised restoration philosophy:~\cite{lehtinen2018,kashyap2021n2n,wisdom2020}.
  \item Modular / differentiable audio DSP context:~\cite{engel2020}.
  \item Audio DL and compact waveform cells:~\cite{purwins2019,stoller2018,macartney2018,jansson2017,luo2019,luo2020dprnn,subakan2021,gong2021ast,ronneberger2015,he2016resnet,vaswani2017}.
  \item NAS / RL controllers / PPO:~\cite{elsken2019,zoph2017nas,pham2018,schulman2017,tan2019mnasnet,liu2018pnas}.
  \item Evolutionary NAS and population HPO:~\cite{real2017large,real2019,jaderberg2017,snoek2012,hansen2016cmaes}.
  \item ERL hybrid outer loop:~\cite{khadka2018}.
  \item MoE soft gating prior:~\cite{shazeer2017}.
\end{itemize}

\paragraph{Screened (contrast only).}
\begin{itemize}
  \item \textbf{MAML}~\cite{finn2017}: bi-level / fast-adaptation framing. We do not differentiate through a deep task network. Inner fits are coordinate-style updates on bake parameters. Outer rank is residual $R$.
  \item \textbf{DARTS}~\cite{liu2019}: continuous relaxation of architecture search. We keep discrete ops + small cells under residual scoring.
  \item \textbf{Demucs / Hybrid Demucs / realtime waveform enhancement}~\cite{dfossez2019,dfossez2021,dfossez2020}: strong separators and enhancers, but full multi-scale / hybrid STFT stacks are too heavy per meta trial under overnight bake budgets.
  \item \textbf{DiffWave}~\cite{kong2021}: diffusion vocoder. Screened as a generative sampling stack outside the seam bake operator set.
  \item \textbf{SEGAN-style adversarial enhancement}~\cite{pascual2017}: optional tiny adversarial cues only. Full GAN training loops screened for per-trial cost.
\end{itemize}

\paragraph{Positioning.}
Relative to this map, the present work contributes (i)~a prolonged residual objective for periodic seam denoising, (ii)~an explicitly hybrid RL+GA(+PBT) meta-outer loop with honest branch naming, and (iii)~a used/screened literature protocol with downloaded source PDFs.
Claims stay inside cycle-local seam restoration under a declared compute budget.
The primary claim is protocol-level: residual-scored meta-search for cycle-local audio denoise operators.
